\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}

\title{3D Visualization and Tracking of Brain fMRI Scans\\\progname}

\author{Nada Elmasry\authname}

\date{19 Jan 2024}

\begin{document}

\maketitle

\section{Problem Statement}
 
\subsection{Problem}
The project aims to implement a user-friendly platform for visualizing 3D fMRI scans.
The program's primary goal is to enable users to visualize brain fMRI scans and track
the activity of a selected brain region throughout an fMRI scan, facilitating a better
understanding of how specific brain regions' activities change over time and in relation to other brain areas.

\subsection{Inputs and Outputs}
The application will take NIFTI or DICOM format files of a patient scan as input.
Subsequently, it will generate a 3D reconstruction of the input along with associated
2D slices in the sagittal, axial, and coronal planes. In addition to viewing the 3D Volume,
users can select a 2D slice and choose the axis for viewing. For tracking a specific region's
activity, users can select the region through an application option, allowing the program to mark the region 
and track its activity over time.



\subsection{Stakeholders}
Stakeholders include but are not limited to researchers, professors, doctors, 
radiologists, medical professionals, and students studying the brain and associated 
diseases and conditions.


\subsection{Environment}
The project will be developed as a cloud-deployed web application, providing users
with a self-contained, cross-platform solution.

\section{Goals}
\begin{enumerate}
\item 3D reconstruction of fMRI scans.
\item Implement 2D slice views (sagittal, axial, coronal) for fMRI scans.
\item Segment and track the activity of a selected brain region.
\item Develop a user-friendly web application.
\end{enumerate}

\section{Stretch Goals}
Implementation of multi-thread processing or GPU processing to enhance computational 
speed and reduce loading times when initially loading a scan, contributing to an optimized user experience.


\end{document}